Blocking-resistant communication through high-value web services

### 2014-07-08 docs/meek.tex
Latency measurement attack.

% \section{Security}

% Google can deanonymize you, because they are the first hop,
% and also often the last hop because of their popularity.

>>>>

\section{Security}

Domain fronting shares a weakness with decoy routing,
which is that the overt and covert destinations lie on different
network paths.
The difference in paths may create side channels---latency measurements for instance---that
enable the censor to
distinguish fronted traffic from traffic that is truly destined
to the front domain.
For example, a CDN can be expected to have responses
to some fraction of requests already in cache,
and respond to those requests with low latency.
Fronted traffic, on the other hand, always continues all the way
to the origin server after reaching the CDN (as if nothing were ever cached),
resulting in a higher latency.
Latency measurement was applied to decoy routing by Schuhard et~al.~\cite[Section~5]{ccs2012-decoys},
who compared empirical round-trip-time distributions using a
Kolmogorov--Smirnov test.
% time between ChangeCipherSpec and ApplicationData

% Edge servers within the censored region.
% Censor could block on the way to the origin server,
% if the censor has visibility to it.
% Maybe the CDN has its own private high-speed cables,
% or it VPNs its own stuff or something.

% Firefox plugin uses normal browser trust store.
% Adversary controls CAs. Can MITM and read your tag and block you.
% Maybe not willing to risk getting caught in MITM.
% Could conceivably send cover traffic if MITM detected, but blah.
